### 2021-03-08 paper/localpsf.tex
todo lists for paper from meeting

% REQUIRED
\begin{abstract}
  We present an efficient matrix-free method for approximating locally translation invariant operators that have locally supported non-negative integral kernels. The idea of the method is to compute impulse responses of the operator at a collection of scattered points, then interpolate these computed impulse responses to approximate impulse responses at other arbitrary points. This results in a product-convolution approximation, which we convert to hierarchical matrix format. Once the approximation is represented in hierarchical matrix format, we perform matrix inversion and other matrix operations using fast hierarchical matrix arithmetic. Impulse responses are computed by applying the operator to a small number of Dirac comb ``batches'' of point sources. A key innovation of our method is a matrix-free procedure for choosing as many points as possible per batch, while ensuring that the supports of the impulse responses within each batch do not overlap. We apply the method to approximate Hessians in large-scale PDE-constrained inverse problem with highly informative data. Numerical results demonstrate that our method substantially outperforms existing state-of-the-art Hessian approximation methods which are based on low-rank approximation. Our method is able to form high quality approximations of high rank Hessians using only a small number of Hessian matrix-vector products.
\end{abstract}

@@

@@

>>>>

% REQUIRED
\begin{abstract}
  We present an efficient matrix-free method for approximating locally translation invariant operators that have locally supported non-negative integral kernels. The idea of the method is to compute impulse responses of the operator at a collection of scattered points, then interpolate these computed impulse responses to approximate impulse responses at other arbitrary points. This results in a product-convolution approximation, which we convert to hierarchical matrix format in order to solve linear systems and perform other matrix operations efficiently using fast hierarchical matrix arithmetic. Impulse responses are computed by applying the operator to a small number of Dirac comb ``batches'' of point sources. A key innovation of our method is a matrix-free procedure for choosing as many points as possible per batch, while ensuring that the supports of the impulse responses within each batch do not overlap. We apply the method to approximate Hessians in large-scale PDE-constrained inverse problem with highly informative data. Numerical results demonstrate that our method substantially outperforms existing state-of-the-art Hessian approximation methods which are based on low-rank approximation. Our method is able to form high quality approximations of high rank Hessians using only a small number of Hessian matrix-vector products.
\end{abstract}

@@

\subsection{Computational cost}

\begin{itemize}
	\item computational complexity in terms of PDE solves:
	\item cost of global low rank approximation (data scalability)
	\item cost to build approximation
	\item cost without compression to do a solve
	\item cost with compression to do a solve
	\item computational complexity for H-matrix alone vs. prod-conv + h-matrix $O(C k^2 \log N)$ PDE solves, C is big, k is big. Here $10$
	\item HODLR: C is smaller, but k is bigger, vs. H1 peeling process
	\item H-matrix operations cost for our method solve
	\item irregular grid
\end{itemize}

@@

\begin{itemize}
	\item GLR vs PCH diffusion time (H)
	\item GLR vs PCH number of obs (Computational cost) (S)
	\item GLR vs PCH aspect ratio (CC) (S)
	\item mesh scalability of PCH (CC) (H)
	\item spectrum plots $P^{-1} H - I$ (Quality of approximation) (H, not Stokes?)
	\item number of krylov iterations: reg precond vs PCH (where?) (H)
	\item turn on preconditioner after number of krylov iterations exceeds 15 in an iteration. Rebuild "as needed". (H)
	\item $P - H = USV^T$ <- less good
	\item $P^{-1} H - I = USV^T$ <- better
	\item true parameter (H)
	\item deterministic reconstruction (H)
	\item noisy measurements (1\% noise). $u|_\text{top}$ (H)
	\item recovered state at top (H)
\end{itemize}
